---
title: "AirBnB Data Analytics (Boston, MA)"
author: "Aisha Elamah"
date: "2023-03-02"
output: html_document
---
# working with the Boston, MA AirBnB dataset to find insghts on 
#customer behaviour.
# firstly unwanted columns will be deleted. Only data necessary for this analysis will be left.
```{r}
list <-listings2 %>%
  select(-c(3,4,8,9,11,12,13,16,17,18,19,20,21,28,29,35,
                     39,40,41,42,43,45,48))
head(list)
```

#cleaning data. removing N/A values, checking for duplicates.

```{r}
str(list)
duplicated(list)
head(list)
```
  #removing missing data


```{r}

list <- na.omit(list)
unique_names <- unique(list$property_type)
head(list)
```
#looking at data for the top 5 booked AirBnB based on neighbourhoods.
```{r}
list2 <- list %>%
  group_by(neighbourhood_cleansed) %>%
  summarise(count = n()) %>%
  top_n(n = 5, wt = count)

ggplot(list2, aes(x=neighbourhood_cleansed, y=count))+
  geom_bar(stat = "identity")

```

#using the Min & Max function to find the most expensive and the least expensive fees for AirBnB in Boston MA

```{r}
print(max(list$price))
print(min(list$price))
```

#looking up the most AirBnB bookings based on the type of property. The most popular neighbourhoods appear to be on average the cheapest neighbourhoods.

```{r}
list3 <- list %>%
  group_by(property_type) %>%
  summarise(count = n()) %>%
  top_n(n = 10, wt = count)

ggplot(list3, aes(x=count, y=property_type))+
  geom_bar(stat = "identity")

```

# in order to use the mean function for our calculation of average price, the price column has to be cleaned and converted to nueric values.

```{r}
list$price <- as.numeric(gsub("\\$", "", list$price))

head(list)
```

#calculating the average price of top 3 bookings based on neighbourhoods

```{r}
top_5_cheapest <- list %>%
  group_by(neighbourhood_cleansed) %>%
  summarize(avg_price = mean(price)) %>%
  arrange(avg_price) %>%
  slice_head(n = 3)
ggplot(top_5_cheapest, aes(x=avg_price, y=neighbourhood_cleansed))+
  geom_bar(stat = "identity")
```




#looking at the availabilty of AirBnB spaces in the various neighbourhoods.
```{r}
df_summary <- list %>% group_by(neighbourhood_cleansed) %>% 
  summarize(total_available = sum(availability_365))

print(df_summary)

ggplot(df_summary, aes(x = neighbourhood_cleansed, y = total_available)) + 
  geom_bar(stat = "identity") +
  labs(title = "Total Available Days by Neighborhood", x ="total available " , y = "neighborhood_cleansed")




```


